### 2009-03-21 doc/storage_system/arc-storage-documentation.tex
Added description of fuse module and examples for fuse module and arcdmc

TODO: what is the FUSE module, how does it work, how can we use it

@@

TODO: Some example of uploading, downloading and stat files, anything more?

>>>>

The \textbf{FUSE module} provides a high-level access to the storage system. Filesystem in Userspace (FUSE) provides a simple library and a kernel-userspace interface. Using FUSE and the ARC Python interface, the FUSE module allows users to mount the storage namespace into the local namespace, enabling the use of, e.g., graphical file browsers. Currently no delegation handling is implemented in the fuse module, so that to change ownership, group access, etc., you need to use the \verb!arc_storage_cli!.

As for the \verb!arc_storage_cli! the credentials of the user and the URL of the Bartender can be configured either with an XML file located at \verb!~/.arc/client.xml! or with environment variables. See Section \ref{sub:prototype_cli_tool} for user configuration.

An example of uploading, downloading and list files with FUSE:

\begin{verbatim}
$ python arcfs.py ./mnt
$ cat testfile
This is a test file
$ mkdir mnt/tmp
$ cp testfile mnt/tmp
$ ls -l mnt/tmp/testfile
-rw-r--r-- 1 jonkni jonkni 20 2009-03-21 23:27 mnt/tmp/testfile
$ cp mnt/tmp/testfile newfile
$ cat newfile
This is a test file
$ cat mnt/tmp/testfile
This is a test file
$ fusermount -u ./mnt
\end{verbatim}

@@

Example of uploading, downloading and list files:

\begin{verbatim}
$ cat testfile
This is a test file
$ arccp testfile arc:///tmp/testfile
$ arcls -l arc:///tmp/testfile
testfile file * * * *
$ arccp arc:///tmp/testfile newfile
$ cat newfile
This is a test file
\end{verbatim}
